EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-06 draft.tex
More comments addressed

% This is the second level? - JJ
In either level, algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.

% This is probably accessory. What difference would it make to upload it to GitHub?
% You also need to say in this section how it helps your overall objective. 
% Does it contribute to reproducibility? We've talked about that elsewhere. 
% Does it help diversity by making easy to add new algorithms? - JJ

@@

After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format as shown in Listing \ref{code:exp}.

\begin{lstlisting}[language=Python, caption=Experiment configuration example, label=code:exp]
{
"DIM_CONFIGURATION" : 
 {
 "2":{"GEN":40,"POP_SIZE": 50,"MAX_ITER":10,"MESSAGES":10},
 "3":{"GEN":25,"POP_SIZE": 60,"MAX_ITER":20,"MESSAGES":10},
 "5":{"GEN":28,"POP_SIZE": 60,"MAX_ITER":30,"MESSAGES":10},
 "10":{"GEN":50,"POP_SIZE": 70,"MAX_ITER":30,"MESSAGES":10},
 "20":{"GEN":66,"POP_SIZE":100,"MAX_ITER":30,"MESSAGES":10},
 "40":{"GEN":80,"POP_SIZE":125,"MAX_ITER":40,"MESSAGES":10}
 },
"GA_WORKER_RATIO" : 0.5,
"FUNCTIONS": [4],
"DIMENSIONS" : [2, 3, 5, 10, 20, 40],
"CXPB_RND": [0.2, 0.6],
"MUTPB_RND": [0.1, 0.3]
}
\end{lstlisting}

>>>>

% This is the second level? - JJ

On either level of integration, algorithm developers can upload the container
definition or images directly to a public repository like DockerHub. Another
option is to upload the container image definition (Dockerfile) to GitHub and
define a trigger to re-upload the image to the registry after an update. Having
images publicly available can contribute to the reproducibility of experiments.
Moreover, having more algorithms available can benefit researchers trying to
compare against other algorithms or increase the diversity of their algorithms
by adding more search methods. Finally, in some cloud services, having hosted 
images is a requirement, as it is the case of Amazon ECS.

% This is probably accessory. What difference would it make to upload it to GitHub?
% You also need to say in this section how it helps your overall objective. 
% Does it contribute to reproducibility? We've talked about that elsewhere. 
% Does it help diversity by making easy to add new algorithms? - JJ
% Explain it a bit more - M

@@

After starting the application, users can push several Experiment Definition 
files at a time and start monitoring the current execution in the terminal.
After an experiment is finished, the user must execute another script
that takes as argument the experiment id to generate a collection of files containing all the
data generated by the experiment, again in a JSON format. An example of an 
experiment definition is shown in Listing \ref{code:exp}. We give more details about the 
data contained in the file in the next section.

\begin{lstlisting}[language=Python, caption=Experiment definition example, label=code:exp]
{
"DIM_CONFIGURATION" : 
 {
 "2":{"GEN":40,"POP_SIZE": 50,"MAX_ITER":10,"MESSAGES":10},
 "3":{"GEN":25,"POP_SIZE": 60,"MAX_ITER":20,"MESSAGES":10},
 "5":{"GEN":28,"POP_SIZE": 60,"MAX_ITER":30,"MESSAGES":10},
 "10":{"GEN":50,"POP_SIZE": 70,"MAX_ITER":30,"MESSAGES":10},
 "20":{"GEN":66,"POP_SIZE":100,"MAX_ITER":30,"MESSAGES":10},
 "40":{"GEN":80,"POP_SIZE":125,"MAX_ITER":40,"MESSAGES":10}
 },
"GA_WORKER_RATIO" : 0.5,
"FUNCTIONS": [4],
"DIMENSIONS" : [2, 3, 5, 10, 20, 40],
"CXPB_RND": [0.2, 0.6],
"MUTPB_RND": [0.1, 0.3]
}
\end{lstlisting}
